---
title: "Data preparation"
date: "August, 2019"
---

```{r setup_preparation, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos =  "h")
knitr::opts_knit$set(root.dir = "../")

# loading required libraries

```

```{r scripts_data_preparation, include=FALSE}
# loading required steps before performing the analysis

```

# Using a step by step approach

Before starting the analysis for the {{__myproject__}}, a few important steps were taken in order to prepare the source data files. These steps are listed below:

- **Step 01**: Create Functions;
- **Step 02**: Data Ingestion;
- **Step 03**: Data Cleaning;
- **Step 04**: Label Translation;
- **Step 05**: Data Enhancement;
- **Step 06**: Dataset Preparation.

*******************************************************************************

# Create Functions (step 1)
This step create functions to be used in the next steps. Following, all functions created are described.

## Specific data ingestion functions

### Function 1
Description of function 1.

``` {r function_1_name, eval = FALSE}
# Function 1 code
```

### Function 2
Description of function 2.

``` {r function_2_name, eval = FALSE}
# Function 2 code
```

### Function 3
Description of function 3.

``` {r function_3_name, eval = FALSE}
# Function 3 code
```

### Function n
Description of function n.

``` {r function_n_name, eval = FALSE}
# Function n code
```